Trends of SDR in Thessaloniki

### 2023-06-16 Article.Rmd
Commit 2023-06-16 13:17

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:          false
numbersections:       true
header-includes:
   - \usepackage{subfig}
output: 
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
# date:           "`r format(Sys.time(), '%F')`"
---

@@

expanded discription

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.33\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

```{r szatrends2, results="asis", echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat("\\ \\ \n")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

@@

```{r seasonalALL, echo=F, fig.cap="Trends by season for All-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Trends by season for Clear-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Trends by season for Cloudy-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-3.pdf")
```

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:          false
numbersections:       true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  rticles::elsevier_article:
    keep_tex:         true
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
# date:           "`r format(Sys.time(), '%F')`"
---

@@

expanded description

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

@@

```{r seasonalALL, echo=F, fig.cap="Trends by season for all condition. Displaying monthly means of daily means.", out.width="100%"}
knitr::include_graphics("./images/SeasonalTrendsTogether-1.pdf")
```

<!-- ```{r seasonalALL, echo=F, fig.cap="Trends by season for All-sky condition. Displays monthly means of daily means."} -->
<!-- knitr::include_graphics("./images/SeasonalTrends-1.pdf") -->
<!-- ``` -->

<!-- ```{r seasonalCLEAR, echo=F, fig.cap="Trends by season for Clear-sky condition. Displays monthly means of daily means."} -->
<!-- knitr::include_graphics("./images/SeasonalTrends-2.pdf") -->
<!-- ``` -->

<!-- ```{r seasonalCLOUD, echo=F, fig.cap="Trends by season for Cloudy-sky condition. Displays monthly means of daily means."} -->
<!-- knitr::include_graphics("./images/SeasonalTrends-3.pdf") -->
<!-- ``` -->
